Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 paper.Rnw
reknit paper after small changes
knit paper after filtering out tank rash bullets

@@

# Files that will need to be removed once I know how to 
#bullet_train <- read.csv("../data/hamby173and252_train.csv")
no_tank_rash = read.csv("data-no-tank-rash.csv")

# Load the bullet matching training data and make some adjustments:
#   1. filter out observations know to have tank rash
#   2. exclude features not used to train the rtrees random forest 
#   3. change the name of the same_source variable to match the test data
#   4. reorder the variables
bullet_train <-
  read.csv("data-bullet-train.csv") %>%
  slice(no_tank_rash$case) %>%
  #filter(land_id1 == "Hamby173-BrUnk-B2-L1")
  select(-lag,-abs_lag,-signature_length) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())

>>>>

# Save the figure to use in the GitHub repo readme
# ggsave(
#   filename = "figure-readme.png",
#   plot = plot_grid(sine_poi_exp, exp_scatter),
#   width = 12,
#   height = 5
# )

@@

# Load the bullet matching training data and make some adjustments:
#   1. filter out observations known to have tank rash
#   2. exclude features not used to train the rtrees random forest 
#   3. add a case variable
#   4. change the name of the same_source variable to match the test data
#   5. reorder the variables
bullet_train <-
  read.csv("data-bullet-train.csv") %>%
  filter(!(
    land_id1 %in% c(
      "Hamby173-Br6-B2-L1",
      "Hamby173-Br9-B2-L4",
      "Hamby173-BrUnk-BB-L2",
      "Hamby173-BrUnk-B!-L4"
    ) |
      land_id2 %in% c(
        "Hamby173-Br6-B2-L1",
        "Hamby173-Br9-B2-L4",
        "Hamby173-BrUnk-BB-L2",
        "Hamby173-BrUnk-B!-L4"
      )
  )) %>%
  select(-lag, -abs_lag, -signature_length) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())
